The influence of resource use on yield versus sale price trade-off in Australian vineyards

### 2023-11-16 article.tex
all edits done but the introduction

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{The influence of resource use on yield versus quality trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%\affiliation[label1]{organization={QUT},
%  addressline={},
%  city={},
%  postcode={},
%  state={QLD},
%  country={}}
%\affiliation[label2]{organization={AWRI},
%  addressline={},
%  city={},
%  postcode={},
%  state={SA},
%  country={}}
%\affiliation[label3]{organization={Food Agility CRC},
%  addressline={},
%  city={},
%  postcode={},
%  state={Vic},
%  country={}}
\author[label1,label2,label3]{Author}
\date{02/08/2023}
\begin{abstract}
% The word limit needs to be checked.
When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield and quality of the produce. In this analysis we observe relationships between resource use, yield and quality through the use of statistical models. The dataset used for this analysis includes data collected for the past 10 years from 1261 vineyards located over a diverse range of Australian winegrowing regions. Yield and quality (measured as a ratio of sale price to area) was modelled to resource factors related to water usage and emissions. The analysis confirmed an expected strong relationship between size and resource use, with the overall space of a vineyard and its access to resources greatly determining the upper limit of yield. However, size was also negatively related to the average sale price of grapes, we find that higher quality being connected to high resource inputs per area; rather than to the overall expenditure of resources. Regional and yearly effects on Vineyard outputs were also identified. Overall, the analysis highlighted the importance of considering a vineyard's business goal, region, external pressures and economies of scale, with regional constraints also contributing to deciding the best resource use strategies to pursue when considering quality or quantity.
\end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
\begin{highlights}
  \item Comparative analysis of resource use, quality and quantity in Australian winegrowing.
  \item Regional comparison of outcomes and resource use in Australian winegrowing regions.
  \item Baseline models for comparing wine crops.
  \item Analysis of national, decade long data source.
\end{highlights}
\end{frontmatter}

@@

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield versus quality produced. This dilemma exists across agriculture through shared fundamental considerations such as water use and fuel usage \citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. Quality in viticulture (the cultivation of grapes for wine production) is driven through its integration within the wine industry, with the potential quality of a wine being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability within viticulture is further complicated by environmental and socio-demographic pressures \citep{santiago-brownSustainabilityAssessmentWineGrape2015}. In the Australian context, these include biosecurity, climate and international market demands \citep{canadellMultidecadalIncreaseForest2021,longbottomRoleVineyardPractices2015,oliverReviewSoilPhysical2013}.
\par
There is an extensive amount of research into the effects of a variety of factors on grape quality and yield \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022,liakosMachineLearningAgriculture2018}. However, due to the lack of long-term and in-depth data, individual factors are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets restricts the ability to gain statistical insights at large scales and across multiple regions, as a result broader studies are lacking \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data spanning 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We use this dataset to describe the relationship of resources related to water and fuel use with the output yield and quality of the resultant product, taking into account the size and location of the vineyard. The practical addition of this aim is a baseline for comparison: given a vineyard within Australia, one could estimate the comparative efficiency with regard to the tradeoff between invested resources, yield and quality. This is the first time that such a trade off has been confirmed explicitly across such varying regions, scales and climates in the Australian winegrowing industry.
\section{Methods}
\subsection{Data}

@@

Data used in this analysis were obtained from Sustainable Winegrowing Australia and Wine Australia. Sustainable Winegrowing Australia is Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Wine Australia is an Australian Government statutory authority governed by the Wine Australia Act \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.

@@

Predicted variables in this analysis were yield, defined as the total tonnes of grapes harvested, and quality, defined as average sale price of grapes. It is acknowledged that quality can be defined in a variety of ways, for example by the grapes': aroma, chemical composition and color \citep{kasimatiPredictingGrapeSugar2022,mejeanperrotDecisionsupportSystemPredict2022,suarezAssessingWineGrape2021}. Using sale price was based on the reliance of market value of winegrapes on grape quality and because Wine Australia explicitly defines grape quality through the use of discrete price brackets in their annual reports. The generalisation made to reflect quality through using average price assumed a due diligence of those who purchased the grapes \citep{yeggeInfluenceSensoryNonsensory2001}. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

The first subset of data (used for Model 1 and Model 2, see Table \ref{tab:tab1}) contained 5298 samples spanning the period from 2012 to 2022, covering 55 GI Regions and 1261 separate vineyards.

@@

Additional variables were considered for analysis but were excluded due to being either underreported or had insignificant contributions to model accuracies. Variables explored but not used due to low reporting values included fertiliser, and scope two emissions. Variables considered but ultimately removed due to a lack of significant contributions to models, included the use of renewable energy, contractor use, and pressures such as frost, fire and disease.

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{my_map.pdf}}
  \caption{Map of vineyard average income for each of the used GI Regions.}\label{fig:map}
\end{figure}%%

@@

The site of a vineyard predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. Differences in vineyard locations were captured through the use of Geographical Indicator Regions (GI Regions, see Figure \ref{fig:map}) defined by Wine Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each GI Region has its own unique mixture of climatic and geophysical properties that describes a unique winegrowing region within Australia and is a protected trademark under the Wine Australia act \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Both Wine Australia and Sustainable Winegrowing Australia used the same GI Region categorical variable format to describe location.

@@

          {Average Sale Price (AUD)} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\

@@

          $\mbox{Average Sale Price (AUD)} \over \mbox{Area Harvested (ha)}$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule

@@

Pearson Correlation Coefficients of the transformed, centred and scaled variables are shown in Table \ref{tab:pearson_correlation}. All correlations were found to be statistically significant (P $<$ 2.200E-16), and except for 'average price' all variables were positively correlated. With water use, area harvested and emissions being positively correlated to yield, it can be considered that more resources and area are likely to lead to greater yields. Average sale price's negative correlation to yield, water use, area and scope one emissions, indicated that size and fuel separately were not the determining factor for grape quality. The negative correlations are not causal relationships (using more water does not cause lower quality) but relative are measures indicating that using greater amounts of water than others may lead to lower quality.
\par
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}cccccccc@{}}
          \toprule
          \textbf{} & \multicolumn{1}{c}{\textbf{Yield}} & \multicolumn{1}{c}{\textbf{Area Harvested}} & \multicolumn{1}{c}{\textbf{Water Used}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular}}} & \multicolumn{1}{c}{\textbf{Average Price}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular}}} \\ \midrule
          Yield & 1.00 & 0.88 & 0.82 & 0.76 & 0.96 & -0.46 & -0.88 \\
          Area Harvested & 0.88 & 1.00 & 0.78 & 0.83 & 0.73 & -0.19 & -0.81 \\
          Water Used & 0.82 & 0.78 & 1.00 & 0.67 & 0.76 & -0.49 & -0.82 \\
          \begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular} & 0.76 & 0.83 & 0.67 & 1.00 & 0.65 & -0.16 & -0.67 \\
          \begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular} & 0.96 & 0.73 & 0.76 & 0.65 & 1.00 & -0.54 & -0.84 \\
          Average Price & -0.46 & -0.19 & -0.49 & -0.16 & -0.54 & 1.00 & 0.72 \\
          \begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular} & -0.88 & -0.81 & -0.82 & -0.67 & -0.84 & 0.72 & 1.00 \\ \bottomrule
          \end{tabular}}
\end{table}

@@

Each model had a high $R^2$ value, indicating that a most of the variance within the data was described by the models (see Table~\ref{tab:modelsummary}). The models were found to be a good fit, with overall F-tests being statistically significant (P $<$ 2.200E-16). And, aside from 3 variables, F-tests across each model's variables were also significant (with all being at least, P $<$ 0.05). The three exceptions were: scope one emissions in Model 3 (P=0.22) and Model 4 (P=0.0.39), and the interaction between area harvested and water used in model 2 (P=0.22). Note that, scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values and because it was strongly correlated to the response variable in every model (except model 5); especially for Models 1 and 4 (Table \ref{tab:pearson_correlation}). 
%A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par
\begin{table}[]
  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 1\\ \end{tabular}} & 0.9072 & 0.9061 & 775.3 & 2.200e-16 & 0.3065 & 491.3 & 0.1 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 2\\ \end{tabular}} & 0.8291 & 0.8141 & 55.07 & 2.200e-16 & 0.4312
           & 905.03 & 0.19 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 3\\ \end{tabular}} &0.9753 &0.9748 & 1885 & 2.200e-16 & 0.1589 & 71.11 & 0.03 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ \end{tabular}} & 0.9091 & 0.9006 & 106.1 & 2.200e-16 & 0.3153  & 261.41 & 0.10 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 5\\ \end{tabular}} & 0.9089 & 0.9004 & 107.2 & 2.200e-16 & 0.3155 & 262.04 & 0.10 \\ \bottomrule
          \end{tabular}
        }
\end{table}

Models' continuous variable's coefficient values are summarised in Table \ref{tab:contvar}. Model 1 showed all coefficients except for the intercept were significantly contributing to the model (P < 0.05). Model 2's coefficients were all statistically significant. However, for Models 3, 4 and 5 Scope one emissions did not significantly contribute. And, Model 4 only saw statistically significant contributions from the intercept and water use. Although the coefficient for water use was statistically significant for each model, it did not have the highest value, instead area harvested, being an order of magnitude greater dominated the models. Model 5 was able to achieve a similar $R^2$ to Model 4 without area harvested, having stronger influences from water use and scope one emissions.

@@

Regional differences are summarised in Figure \ref{fig:spider}. The most notable difference is between vineyards within 'Hot' and 'Very Dry' regions (warm inland regions), where little emphasis is put on achieving high average sale prices, instead focussing on larger scale yield. Water Use changes dramatically between these regions as well, with water being a driving force in the mass production of grapes but not necessarily the quality. The warmer and drier regions tend to also cater to larger vineyards, with greater areas.
\par
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{starplots.png}}
  \caption{Radar plot of climatic profile's resource use, yield and average sale price.}\label{fig:spider}
\end{figure}

@@

There was an expected strong relationship between size and resource use, with the overall space of a vineyard and its access to resources greatly determining the upper limit of potential yield. However, size was also inversely related to the potential quality, with higher quality being related to high resource inputs per area; rather than to the overall expenditure of resources. Vineyard outputs were also augmented by regional and yearly affects. Even given regional and yearly changes, there was a strong connection between smaller vineyards and higher quality. This could have been due to the easier management of smaller properties.

@@

Scope one emissions' lack of significance and contribution given its F-statistics, could be indicative that other vineyard activities requiring fuel are not leading factors for a vineyards grape quality. The relationship between yield, value and area was not simply about efficiently producing the most grapes. It is possible that the relationship of scope one emissions between yield and sale price was closely tied to a vineyard's area due to requiring more fuel to address more issues over greater distances. It is difficult to discern the connection of scope one emissions directly, as fuel can be used for a broad category of activities. 

@@

Due to regional differences, different strategies are also  employed across different regions, such as some regions targeting mass production over quality. This is most notable when grouping regions by climate, especially when considering GI Regions in the 'Hot Very Dry' climate (see Figure \ref{fig:yield_vs_value_area}). 

>>>>

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{The influence of resource use on yield versus sale price trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%\affiliation[label1]{organization={QUT},
%  addressline={},
%  city={},
%  postcode={},
%  state={QLD},
%  country={}}
%\affiliation[label2]{organization={AWRI},
%  addressline={},
%  city={},
%  postcode={},
%  state={SA},
%  country={}}
%\affiliation[label3]{organization={Food Agility CRC},
%  addressline={},
%  city={},
%  postcode={},
%  state={Vic},
%  country={}}
\author[label1,label2,label3]{Author}
\date{02/08/2023}
\begin{abstract}
% The word limit needs to be checked.
When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield and sale price of the produce. In this analysis we observe relationships between resource use, yield and sale price through the use of statistical models. The dataset used for this analysis includes data collected for the past 10 years from 1261 vineyards located over a diverse range of Australian winegrowing regions. Yield and sale price was modelled to resource factors related to water use and Green House Gas (GHG) emissions. The analysis confirmed a strong relationship between area and resource use, with the overall area of a vineyard and its access to resources greatly determining the upper limit of yield. However, area was also negatively related to the average sale price of grapes, we find that higher average sale prices were connected to high resource inputs per area; rather than to the overall expenditure of resources. Regional and temporal effects on vineyard yield and average sales price were also identified. Overall, the analysis highlighted the importance of considering a vineyard's business goal, region, external pressures and economies of scale, when considering whether to pursue higher yields or average sales prices.
\end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

%\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
%\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC{} 0000 \sep{} 1111
%\end{keyword}
%%Research highlights
\begin{highlights}
  \item Comparative analysis of resource use, average sale price and quantity in Australian winegrowing.
  \item Regional comparison of outcomes and resource use in Australian winegrowing regions.
  \item Baseline models for comparing vineyards.
  \item Analysis of national, decade long data source.
\end{highlights}
\end{frontmatter}

@@

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. 
% When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield versus quality produced. 
% TODO: fix paper justifiction.
% NOTE: This introduction does just need a bit of work.

% Using sale price was based on the reliance of market value of winegrapes on grape quality and because Wine Australia explicitly defines grape quality through the use of discrete price brackets in their annual reports. The generalisation made to reflect quality through using average price assumed a due diligence of those who purchased the grapes \citep{yeggeInfluenceSensoryNonsensory2001}.

A dilemma exists across agriculture through shared fundamental considerations such as water use and fuel usage \citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. The average price of grapes for wine production is driven through its integration within the wine industry. An important connection between grapes and their price is the grapes perceived quality, which initially defines a wines potential through the grapes chemical makeup \citep{blackTerpenoidsTheirRole2015,schreierFlavorCompositionWines1979}. Grapes of higher of percieved higher quality or from particularly famour regions will garner different prices \citep{wineaustraliaNationalVintageReport2021}. The consideration of sustainability within viticulture is further complicated by environmental and socio-demographic pressures \citep{santiago-brownSustainabilityAssessmentWineGrape2015}. In the Australian context, these include biosecurity, climate and international market demands \citep{canadellMultidecadalIncreaseForest2021,longbottomRoleVineyardPractices2015,oliverReviewSoilPhysical2013}.
\par
There is an extensive amount of research into the varied effects of factors on grape quality and yield \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022,liakosMachineLearningAgriculture2018}. However, due to the lack of long-term and in-depth data, individual factors are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets restricts the ability to gain statistical insights at large scales and across multiple regions, as a result broader studies are lacking \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data spanning 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We use this dataset to describe the relationship of resources related to water and fuel use with the output yield and average sale price of the resultant product, taking into account the size and location of the vineyard. The practical addition of this aim is a baseline for comparison: given a vineyard within Australia, one could estimate the comparative efficiency with regard to the tradeoff between invested resources, yield and average sale price. This is the first time that such a trade off has been confirmed explicitly across such varying regions, scales and climates in the Australian winegrowing industry.
\section{Methods}
\subsection{Data}

@@

Data used in these analyses were obtained from Sustainable Winegrowing Australia and Wine Australia. Sustainable Winegrowing Australia is Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data collected by Sustainable Winegrowing Australia is entered voluntarily by winegrowers at the end of harvest. Wine Australia is an Australian Government statutory authority governed by the Wine Australia Act \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Data collected by Wine Australia is publicly available.

@@

Predicted variables in this analysis were yield, defined as the total tonnes of grapes harvested, and average sale price of grapes. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

The first subset of data (used for Model 1 and Model 2, see Table \ref{tab:tab1}) contained 5298 samples spanning the period from 2012 to 2022, covering 55 GI Regions and 1261 discrete vineyards.

@@

Additional variables were considered for analysis but were excluded due to being either underreported or had insignificant contributions to model accuracies. Variables explored but not used due to low reporting values included fertiliser, electricity, and scope two emissions. Variables considered but ultimately removed due to a lack of significant contributions to models, included the use of renewable energy, contractor use, and pressures such as frost, fire and disease.

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{my_map.pdf}}
  \caption{Map of each GI Regions average income for a vineyard of that region (average grape sale price per tonne $\times$ total tonnes yielded).}\label{fig:map}
\end{figure}%%

@@

The site of a vineyard predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape yield and average sale price \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. Differences in vineyard locations were captured through the use of Geographical Indicator Regions (GI Regions, see Figure \ref{fig:map}) defined by Wine Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each GI Region has its own unique mixture of climatic and geophysical properties that describes a unique winegrowing region within Australia and is a protected trademark under the Wine Australia act \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Both Wine Australia and Sustainable Winegrowing Australia used the same GI Region categorical variable format to describe location.

@@

          {Average Sale Price (AUD/tonne)} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\

@@

          $\mbox{Average Sale Price (AUD/tonne)} \over \mbox{Area Harvested (ha)}$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule

@@

Pearson Correlation Coefficients of the transformed, centred and scaled variables are shown in Table \ref{tab:pearson_correlation}. All correlations were found to be statistically significant (P $<$ 2.200E-16), and except for 'average price' all variables were positively correlated. With water use, area harvested and emissions being positively correlated to yield, it can be considered that more resources and area are likely to lead to greater yields. Average sale price's negative correlation to yield, water use, area and scope one emissions, indicated that size and fuel separately were not the determining factor for average sale price. The negative correlations are not causal relationships but relative (using more water does not cause lower sale prices).
\par
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}cccccccc@{}}
          \toprule
          \textbf{} & \multicolumn{1}{c}{\textbf{Yield}} & \multicolumn{1}{c}{\textbf{Area Harvested}} & \multicolumn{1}{c}{\textbf{Water Used}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular}}} & \multicolumn{1}{c}{\textbf{Average Price}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular}}} \\ \midrule
          Yield & 1.00 & 0.88 & 0.82 & 0.76 & 0.96 & -0.46 & -0.88 \\
          Area Harvested & 0.88 & 1.00 & 0.78 & 0.83 & 0.73 & -0.19 & -0.81 \\
          Water Used & 0.82 & 0.78 & 1.00 & 0.67 & 0.76 & -0.49 & -0.82 \\
          \begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular} & 0.76 & 0.83 & 0.67 & 1.00 & 0.65 & -0.16 & -0.67 \\
          \begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular} & 0.96 & 0.73 & 0.76 & 0.65 & 1.00 & -0.54 & -0.84 \\
          Average Price & -0.46 & -0.19 & -0.49 & -0.16 & -0.54 & 1.00 & 0.72 \\
          \begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular} & -0.88 & -0.81 & -0.82 & -0.67 & -0.84 & 0.72 & 1.00 \\ \bottomrule
          \end{tabular}}
\end{table}

@@

Each model had a high $R^2$ value, indicating that most of the variance within the data was described by the models (see Table~\ref{tab:modelsummary}). The models were found to be a good fit, with overall F-tests being statistically significant (P $<$ 2.200E-16). And, aside from 3 variables, F-tests across each model's variables were also significant (with all being at least, P $<$ 0.05). The three exceptions were: scope one emissions in Model 3 (P=0.22) and Model 4 (P=0.0.39), and the interaction between area harvested and water used in model 2 (P=0.22). Note that, scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values and because it was strongly correlated to the response variable in every model (except model 5); especially for Models 1 and 4 (Table \ref{tab:pearson_correlation}). 
%A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par
\begin{table}[]
  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 1\\ \end{tabular}} & 0.9072 & 0.9061 & 775.3 & 2.200e-16 & 0.3065 & 491.3 & 0.1 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 2\\ \end{tabular}} & 0.8291 & 0.8141 & 55.07 & 2.200e-16 & 0.4312
           & 905.03 & 0.19 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 3\\ \end{tabular}} &0.9753 &0.9748 & 1885 & 2.200e-16 & 0.1589 & 71.11 & 0.03 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ \end{tabular}} & 0.9091 & 0.9006 & 106.1 & 2.200e-16 & 0.3153  & 261.41 & 0.10 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 5\\ \end{tabular}} & 0.9089 & 0.9004 & 107.2 & 2.200e-16 & 0.3155 & 262.04 & 0.10 \\ \bottomrule
          \end{tabular}
        }
\end{table}

Models' continuous variable's coefficient values are summarised in Table \ref{tab:contvar}. Model 1 showed all coefficients except for the intercept were significantly contributing to the model (P < 0.05). Model 2's coefficients were all statistically significant. However, for Models 3, 4 and 5 scope one emissions did not significantly contribute. And, Model 4 only saw statistically significant contributions from the intercept and water use. Although the coefficient for water use was statistically significant for each model, it did not have the highest value, instead area harvested, being an order of magnitude greater dominated the models. Model 5 achieved a similar $R^2$ to Model 4 without area harvested, having stronger influences from water use and scope one emissions.

@@

Regional differences are summarised in Figure \ref{fig:spider}. The most notable difference is between vineyards within 'Hot' and 'Very Dry' regions (warm inland regions), where high average sale prices are historically low, and yield is high. Water Use changes dramatically between these regions as well, with water being a driving force for yield but not necessarily average sale price. The warmer and drier regions tend to also have larger vineyards.
\par
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{starplots.png}}
  \caption{Radar plot of climatic profile's resource use, yield and average sale price. The left reflects vineyards in different climatic temperatures. The right reflects vineyards in different rainfall climates.}\label{fig:spider}
\end{figure}

@@

There was an expected strong relationship between size and resource use, with the overall area of a vineyard and its access to resources greatly determining the upper limit of potential yield. However, size was also inversely related to the potential average sale price, with higher sales prices being related to high resource inputs per area; rather than to the overall expenditure of resources. Vineyard yields and sales price changed greatly by region and year. Even given regional and yearly changes, there was a strong connection between smaller vineyards and higher sales prices. This could have been due to more attention available when managing smaller properties.

@@

The lack of significance of scope one emissions and its contribution to models, given its F-statistics, could be indicative that other vineyard activities requiring fuel are not leading factors for a vineyards avereage sale price. The relationship between yield, value and area was not simply about efficiently producing the most grapes. It is possible that the relationship of scope one emissions between yield and sale price was closely tied to a vineyard's area due to requiring more fuel to address more issues over greater distances. It is difficult to discern the connection of scope one emissions directly, as fuel can be used for a broad category of activities. 

@@

Due to regional differences, different strategies are also  employed across different regions, such as some regions targeting mass production over higher sales price. This is most notable when grouping regions by climate, especially when considering GI Regions in the 'Hot Very Dry' climate (see Figure \ref{fig:yield_vs_value_area}). 
